Near Optimal Behavior via Approximate State Abstraction

### 2016-05-22 paper/paper.tex
Starting to unify notation
Added new definition command and starting to unify notation more
Notation for Lemma 1 fixed
Switched from perfect to exact abstraction and other changes to introduction
adding amssymb
put notes back in, small edits to theory
Incorporated michael and stefanie comments
More widow line
Compiling now...
Added gamma used and fixed typo in paper.tex comment
prepping for merge

\documentclass{article}
\usepackage{times}
\usepackage{graphicx}
\usepackage{subfigure} 
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amsthm}%For stating numbered theorems
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{subfigure}
\usepackage{hyperref}
\newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
\usepackage{icml2016/icml2016} 
\usepackage[nolist]{acronym} % Acronym package -- give argument <dua> to suppress acronym usage

%Theorem declarations
\newtheorem{thm}{Theorem}
\newtheorem{lma}{Lemma}
\newtheorem{clm}{Claim}
\newtheorem{defn}{Definition}

\icmltitlerunning{Near Optimal Behavior with Approximate State Abstraction}

% --- Notation Commands ---
\newcommand{\ep}{\widetilde \phi}
\newcommand{\epQ}{\ep_{Q^*}}
\newcommand{\epM}{\ep_{\text{model}}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\mcS}{\mathcal{S}}
\newcommand{\mcT}{\mathcal{T}}
\newcommand{\mcR}{\mathcal{R}}
\newcommand{\pM}{\phi_{\text{model}}}

@@

@@

\twocolumn[
% Suboptimality Bounds for Approximate State Abstraction
\icmltitle{Near Optimal Behavior with Approximate State Abstraction}

% Paper Meta Info
\icmlauthor{David Abel}{david_abel@brown.edu}
\icmladdress{Brown University,
            115 Waterman Street, Providence, RI 02906}
\icmlauthor{D. Ellis Hershkowitz}{david_hershkowitz@brown.edu}
\icmladdress{Brown University,
            115 Waterman Street, Providence, RI 02906}
\icmlauthor{Michael L.\ Littman}{michael_littman@brown.edu}
\icmladdress{Brown University,
            115 Waterman Street, Providence, RI 02906}

\icmlkeywords{Reinforcement Learning, State Aggregation, State Abstraction, Planning, MDP}

\vskip 0.3in
]

@@

% ---------------------------------------
% --- SECTION: Background ---
% ---------------------------------------
\input{background.tex}

@@

@@

% ------------------------------------------------------------------------------------
% --- SECTION: Approximate Abstraction on Example Domains ---
% ------------------------------------------------------------------------------------
\input{results_discussion.tex}

@@

% --- BIBLIOGRAPHY ---
\bibliographystyle{icml2016/icml2016}
\bibliography{state_abs}

>>>>

\documentclass{article}
\usepackage{times}
\usepackage{graphicx}
\usepackage{subfigure} 
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}%For stating numbered theorems
\usepackage{amsfonts}
\usepackage{algorithmic}
\usepackage{subfigure}
\usepackage{hyperref}
\newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
\usepackage[accepted] {icml2016/icml2016}
\usepackage[nolist]{acronym} % Acronym package -- give argument <dua> to suppress acronym usage

%Theorem declarations
\newtheorem{thm}{Theorem}
\newtheorem{lma}{Lemma}
\newtheorem{clm}{Claim}

\newtheoremstyle{dotless}{}{}{\itshape}{}{\bfseries}{}{ }{}
\theoremstyle{dotless}
\newtheorem{defn}{Definition}

\newcommand{\bdefn}[1]{
\begin{defn} {\boldmath (#1)}\textbf{:}
}

\newcommand{\edefn}[1]{
\end{defn}
}

%\icmltitlerunning{Near Optimal Behavior via Approximate State Abstraction}

% --- Notation Commands ---
\newcommand{\ep}{\widetilde \phi}
\newcommand{\epQ}{\ep_{Q^*}}
\newcommand{\epB}{\ep_{\text{bolt}}}
\newcommand{\epMu}{\ep_{\text{mult}}}
\newcommand{\epM}{\ep_{\text{model}}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\mcS}{\mathcal{S}}
\newcommand{\mcT}{\mathcal{T}}
\newcommand{\mcR}{\mathcal{R}}
\newcommand{\mcA}{\mathcal{A}}
\newcommand{\pM}{\phi_{\text{model}}}

@@

%\newcommand\dnote[1]{\textcolor{blue}{\vspace{-1mm}}}
%\newcommand\enote[1]{\textcolor{green}{\vspace{-1mm}}}

@@

\twocolumn[
% Suboptimality Bounds for Approximate State Abstraction
\icmltitle{Near Optimal Behavior via Approximate State Abstraction}

\begin{center}
\large{\it To appear at ICML 2016}
\end{center}

% Paper Meta Info
\icmlauthor{David Abel\dagger}{david\_abel@brown.edu}
%\icmladdress{Brown University, 115 Waterman Street, Providence, RI 02906}
\icmlauthor{D. Ellis Hershkowitz\dagger}{david\_hershkowitz@brown.edu}
%\icmladdress{Brown University, 115 Waterman Street, Providence, RI 02906}
\icmlauthor{Michael L.\ Littman}{michael\_littman@brown.edu}
%\icmladdress{Brown University, 115 Waterman Street, Providence, RI 02906}
\icmlkeywords{Reinforcement Learning, State Aggregation, State Abstraction, Planning, MDP}
\vspace{0.3in}
]

@@

% ---------------------------------------
% --- SECTION: Background ---
% ---------------------------------------
\input{mdp_background.tex}

@@

% -----------------------------------------------
% --- SECTION: Abstraction Notion ---
% -----------------------------------------------
\input{abstraction_notation.tex}

@@

% ------------------------------------------------------------------------------------
% --- SECTION: Approximate Abstraction on Example Domains ---s
% ------------------------------------------------------------------------------------
\input{results_discussion.tex}

@@

\newpage
% --- BIBLIOGRAPHY ---
\bibliographystyle{icml2016/icml2016}
\bibliography{state_abs}
